Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-07-27 paper/manuscript.tex
fixing references and contributions

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed figures~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis},and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to introduction and drug discovery sections, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to sections~\ref{sec:theory} and \ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations. Reviewed and edited text throughout.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:prerequisites},4.2, 5.3, 6, 7.2.3, 8.3.1, 8.3.2, 9\\
\textbf{JDC}: Wrote section~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.\\
\textbf{HBM} Contributed to section \ref{sec:plot_data} and figure \ref{fig:scatterplot_analysis} and helped edit the paper.\\
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

>>>>

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed Figs.~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis},and created Figs.~\ref{fig:fig_what_is_lambda},~\ref{fig:fig_what_is_alchemy},~\ref{fig:overlap},~\ref[fig:pmf} and replotted~\ref{fig:automatic-equilibration-detection} and~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: Created Figs~ \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, and an initial draft of~\ref{fig:fig_types_of_networks}. Wrote Sec.~\ref{sec:plot_data}, the checklist Sec.~\ref{sec:checklist}, and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to Sec.~\ref{sec:data_analysis}, provided the data for figure~\ref{fig:overlap}, compiled the dataset for Sec.~\ref{sec:benchmark} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to Sec.~\ref{sec:intro} and~\ref{sec:drugdiscovery}, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to sections~\ref{sec:theory} and~\ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote Sec.~\ref{sec:important_path} describing choices for alchemical pathways and parts of~\ref{sec:data_analysis} on the analysis for free energy calculations. Reviewed and edited text throughout.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to Sec.~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{sec:important_path},~\ref{subsec:estimators},~\ref{subsec:uncertainty}, and~\ref{sec:conclusion}\\
\textbf{JDC}: Wrote Sec.~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed Sec.~\ref{subsec:accuracy}, to Sec.~\ref{sec:relative-fe-protocol}, and to Sec.~\ref{sec:are-they-good}.\\
\textbf{HBM} Contributed to Sec.~\ref{sec:plot_data} and Fig.~ \ref{fig:scatterplot_analysis} and helped edit the paper.\\
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.
